

## ``hc_annotations``
Adding annotations to highcharts objects

#### Description 

Helper function to add annotations to highcharts library.
Usage
hc_annotations(hc, ...)
hc_add_annotation(hc, ...)
hc_add_annotations(hc, x)

#### Arguments 

hc
...
x
A highchart htmlwidget object.
 #### Arguments 
 defined in http://www.highcharts.com/plugin-registry/single/
17/Annotations.
A list or a data.frame of annotations.hc_annotationsOptions

The x elemens must have xValue and yValue elements
hc_annotationsOptions Setting Annotations Options

#### Description 

Setting Annotations Options
Usage
hc_annotationsOptions(hc, ...)
 #### Arguments 

* ``hc ``: A highchart htmlwidget object.
... Options defined in http://www.highcharts.com/plugin-registry/single/
17/Annotations.
hc_chart
Adding chart options to highchart objects

#### Description 

Options regarding the chart area and plot area as well as general chart options.
Usage
hc_chart(hc, ...)
 #### Arguments 

* ``hc ``: A highchart htmlwidget object.
* ``...``: Arguments defined in http://api.highcharts.com/highcharts#chart.40
hc_colorAxis

#### Examples
```{r}
data(citytemp)
hc <- highchart() %>%
hc_xAxis(categories = citytemp$month) %>%
hc_add_series(name = "Tokyo", data = citytemp$tokyo) %>%
hc_add_series(name = "London", data = citytemp$london)
hc %>%
hc_chart(type = "column",
options3d = list(enabled = TRUE, beta = 15, alpha = 15))
hc %>%
hc_chart(borderColor = '#EBBA95',
borderRadius = 10,
borderWidth = 2,
backgroundColor = list(
linearGradient = c(0, 0, 500, 500),
stops = list(
list(0, 'rgb(255, 255, 255)'),
list(1, 'rgb(200, 200, 255)')
)))
```

## ``hc_colorAxis``
Adding Color Axis options to highchart objects

#### Description 

Function to set the axis color to highcharts objects.
Usage
hc_colorAxis(hc, ...)
 #### Arguments 

* ``hc ``: A highchart htmlwidget object.
... Arguments are defined in http://api.highcharts.com/highmaps#colorAxis.
Examples
```{r}
nyears <- 5
df <- expand.grid(seq(12) - 1, seq(nyears) - 1)
df$value <- abs(seq(nrow(df)) + 10 * rnorm(nrow(df))) + 10
df$value <- round(df$value, 2)
ds <- list_parse2(df)
hc <- highchart() %>%
hc_chart(type = "heatmap") %>%
hc_title(text = "Simulated values by years and months") %>%
hc_xAxis(categories = month.abb) %>%
hc_yAxis(categories = 2016 - nyears + seq(nyears)) %>%
hc_add_series(name = "value", data = ds)
hc_colorAxis(hc, minColor = "#FFFFFF", maxColor = "#434348")
hc_colorAxis(hc, minColor = "#FFFFFF", maxColor = "#434348",
type = "logarithmic")
```

```{r}
require("viridisLite")
n <- 4
stops <- data.frame(q = 0:n/n,
c = substring(viridis(n + 1), 0, 7),
stringsAsFactors = FALSE)
stops <- list_parse2(stops)
hc_colorAxis(hc, stops = stops, max = 75)
```
