hc_add_series_ohlc
Shorcut for create candlestick charts

#### Description 

This function helps to create candlestick from xts objects obtaining by getSymbols function from
the quantmod.
Usage
hc_add_series_ohlc(hc, x, type = "candlestick", ...)
 #### Arguments 

* ``hc ``: A highchart htmlwidget object.
x A OHLC object from the quantmod package.
type The type of chart. Can be candlestick or ohlc.
... Aditional shared arguments for the data series (http://api.highcharts.com/
highcharts#series).
Examples
## Not run:
library("xts")
data(sample_matrix)
matrix_xts <- as.xts(sample_matrix, dateFormat = "Date")
head(matrix_xts)hc_add_series_scatter
33
class(matrix_xts)
highchart() %>%
hc_add_series_ohlc(matrix_xts)
library("quantmod")
x <- getSymbols("AAPL", auto.assign = FALSE)
y <- getSymbols("SPY", auto.assign = FALSE)
highchart() %>%
hc_add_series_ohlc(x) %>%
hc_add_series_ohlc(y)
## End(Not run)
hc_add_series_scatter Shorcut for create scatter plots

#### Description 

This function helps to create scatter plot from two numerics vectors. Options argumets like size,
color and label for points are added.
Usage
hc_add_series_scatter(hc, x, y, z = NULL, color = NULL, label = NULL,
showInLegend = FALSE, ...)
 #### Arguments 

* ``hc ``: A highchart htmlwidget object.
x A numeric vector.
y A numeric vector. Same length of x.
z A numeric vector for size. Same length of x.
color A vector to color the points.
label A vector to put names in the dots if you enable the datalabels.
showInLegend Logical value to show or not the data in the legend box.
... Aditional shared arguments for the data series (http://api.highcharts.com/
highcharts#series).34
hc_add_series_times_values
Examples
## Not run:
hc <- highchart()
hc_add_series_scatter(hc,
hc_add_series_scatter(hc,
hc_add_series_scatter(hc,
hc_add_series_scatter(hc,
hc_add_series_scatter(hc,
mtcars$wt,
mtcars$wt,
mtcars$wt,
mtcars$wt,
mtcars$wt,
mtcars$mpg)
mtcars$mpg, mtcars$drat)
mtcars$mpg, mtcars$drat, mtcars$am)
mtcars$mpg, mtcars$drat, mtcars$qsec)
mtcars$mpg, mtcars$drat, mtcars$qsec, rownames(mtcars))
# Add named attributes to data (attributes length needs to match number of rows)
hc_add_series_scatter(hc, mtcars$wt, mtcars$mpg, mtcars$drat, mtcars$qsec,
name = rownames(mtcars), gear = mtcars$gear) %>%
hc_tooltip(pointFormat = "<b>{point.name}</b><br/>Gear: {point.gear}")
## End(Not run)
hc_add_series_times_values
Shorcut for create/add time series from times and values

#### Description 

This function add a time series to a highchart object.
Usage
hc_add_series_times_values(hc, dates, values, ...)
 #### Arguments 

* ``hc ``: A highchart htmlwidget object.
dates A date vector (same length as values)
values A numeric vector
... Aditional arguments for the data series (http://api.highcharts.com/highcharts#
series).
Details
This function modify the type of chart to datetimehc_add_series_treemap
35
Examples
## Not run:
require("ggplot2")
data(economics, package = "ggplot2")
hc_add_series_times_values(hc = highchart(),
dates = economics$date,
values = economics$psavert,
name = "Personal Savings Rate")
## End(Not run)
hc_add_series_treemap Shorcut for create treemaps

#### Description 

This function helps to create higcharts treemaps from treemap objects from the package treemap.
Usage
hc_add_series_treemap(hc, tm, ...)
 #### Arguments 

* ``hc ``: A highchart htmlwidget object.
tm A treemap object from the treemap package.
... Aditional shared arguments for the data series (http://api.highcharts.com/
highcharts#series).
Examples
```{r}
## Not run:
library("treemap")
library("viridis")
data(GNI2014)
head(GNI2014)
tm <- treemap(GNI2014, index = c("continent", "iso3"),
vSize = "population", vColor = "GNI",
type = "comp", palette = rev(viridis(6)),
draw = FALSE)36
hc_add_series_ts
highchart(height = 800) %>%
hc_add_series_treemap(tm, allowDrillToNode = TRUE,
layoutAlgorithm = "squarified",
name = "tmdata") %>%
hc_title(text = "Gross National Income World Data") %>%
hc_tooltip(pointFormat = "<b>{point.name}</b>:<br>
Pop: {point.value:,.0f}<br>
GNI: {point.valuecolor:,.0f}")
## End(Not run)
```

## ``hc_add_series_ts``
Shorcut for create/add time series charts from a ts object

#### Description 

This function add a time series to a highchart object from a ts object.
Usage
hc_add_series_ts(hc, ts, ...)
 #### Arguments 

* ``hc ``: A highchart htmlwidget object.
ts A time series object.
... Aditional arguments for the data series (http://api.highcharts.com/highcharts#
series).
Details
This function modify the type of chart to datetime
```{r}
Examples
## Not run:
highchart() %>%
hc_title(text = "Monthly Airline Passenger Numbers 1949-1960") %>%
hc_subtitle(text = "The classic Box and Jenkins airline data") %>%
hc_add_series_ts(AirPassengers, name = "passengers") %>%
hc_tooltip(pointFormat = '{point.y} passengers')
highchart() %>%
hc_title(text = "Monthly Deaths from Lung Diseases in the UK") %>%
hc_add_series_ts(fdeaths, name = "Female") %>%hc_add_series_xts
hc_add_series_ts(mdeaths, name = "Male")
## End(Not run)
```
## hc_add_series_xts
Shorcut for create highstock chart from xts object

#### Description 

This function helps to create highstock charts from xts objects obtaining by getSymbols function
from the quantmod.
Usage
hc_add_series_xts(hc, x, ...)
 #### Arguments 

* ``hc ``: A highchart htmlwidget object.
x A xts object from the quantmod package.
... Aditional shared arguments for the data series (http://api.highcharts.com/
highcharts#series).
Examples
## Not run:
library("quantmod")
usdjpy <- getSymbols("USD/JPY", src="oanda", auto.assign = FALSE)
eurkpw <- getSymbols("EUR/KPW", src="oanda", auto.assign = FALSE)
highchart(type = "stock") %>%
hc_add_series_xts(usdjpy, id = "usdjpy") %>%
hc_add_series_xts(eurkpw, id = "eurkpw")
## End(Not run)

##``hc_add_theme``
Add themes to a highchart object

#### Description 

Add highcharts themes to a highchart object.
Usage
hc_add_theme(hc, hc_thm)
 #### Arguments 

hc
hc_thm
A highchart object
A highchart theme object ("hc_theme" class)
Examples
```{r}
highchart() %>%
hc_add_series(data = c(7.0, 6.9, 9.5, 14.5, 18.2, 21.5, 25.2,
26.5, 23.3, 18.3, 13.9, 9.6),
type = "column") %>%
hc_add_theme(hc_theme_sandsignika())
```
