---
title: "WVplots"
author: "Kevin O Brien"
date: "13 December 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Package 'WVPlots'
November 6, 2018
Type Package
Title Common Plots for Analysis
Version 1.0.6
Date 2018-11-08
URL https://github.com/WinVector/WVPlots,
https://winvector.github.io/WVPlots/
Maintainer John Mount <jmount@win-vector.com>
BugReports https://github.com/WinVector/WVPlots/issues

#### Description
 Select data analysis plots, under a standardized calling interface implemented
on top of 'ggplot2' and 'plotly'.
Plots of interest include: 'ROC', gain curve, scatter plot with marginal distributions,
conditioned scatter plot with marginal densities,
box and stem with matching theoretical distribution, and density with matching theoretical distribution.
License GPL-3
VignetteBuilder knitr
Depends R (>= 3.4.0)
Imports ggplot2 (>= 2.2.0), wrapr (>= 1.6.3), sigr (>= 1.0.3), cdata
(>= 1.0.3), utils, grid, gridExtra, graphics, mgcv
Suggests knitr, testthat, plotly, hexbin
RoxygenNote 6.1.0
ByteCompile true
NeedsCompilation no
Author John Mount [aut, cre],
Nina Zumel [aut],
Win-Vector LLC [cph]
Repository CRAN
Date/Publication 2018-11-06 18:20:03 UTC
1
2 BinaryYScatterPlot
R topics documented:
BinaryYScatterPlot . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 2
ClevelandDotPlot . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 3
ConditionalSmoothedScatterPlot . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 5
DiscreteDistribution . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 6
DoubleDensityPlot . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 6
DoubleHistogramPlot . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 7
GainCurvePlot . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 8
GainCurvePlotC . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 9
GainCurvePlotWithNotation . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 10
HexBinPlot . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 11
LiftCurvePlot . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 12
LogLogPlot . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 13
PairPlot . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 14
PlotDistCountNormal . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 15
PlotDistDensityBeta . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 16
PlotDistDensityNormal . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 17
PlotDistHistBeta . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 17
plotlyROC . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 18
plot_fit_trajectory . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 19
plot_Keras_fit_trajectory . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 21
PRPlot . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 22
ROCPlot . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 23
ROCPlotPair . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 24
ROCPlotPair2 . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 25
ScatterBoxPlot . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 27
ScatterBoxPlotH . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 28
ScatterHist . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 29
ScatterHistC . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 30
ScatterHistN . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 31
ShadedDensity . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 32
ShadedDensityCenter . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 33
ShadowHist . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 34
ShadowPlot . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 35
WVPlots . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 36
Index 37
BinaryYScatterPlot Plot a scatter plot of a binary variable with smoothing curve.

#### Description

Plot the scatter plot of a binary variable with a smoothing curve.

#### Usage

<pre><code>
BinaryYScatterPlot(frame, xvar, yvar, title, ..., se = FALSE,use_glm = TRUE)
</code></pre> 

#### Arguments

* ``frame``: data frame to get values from
* ``xvar ``:  name of the independent column in frame
* ``yvar``:   name of the dependent (output or result to be modeled) column in frame
* ``title ``:    title to place on plot
* ``... `` : no unnamed argument, added to force named binding of later arguments
* ``se``: if TRUE, add error bars (defaults to FALSE). Ignored if useGLM is TRUE
* ``use_glm``: if TRUE, "smooths" with a one-variable logistic regression (defaults to TRUE)

#### Details

The points are jittered for legibility. By default, a logistic regression fit is used, so that the smoothing
curve represents the probability of y == 1 (as fit by the logistic regression). If ``use_glm`` is set to
FALSE, a standard smoothing curve (either loess or a spline fit) is used.
 
#### Examples
```{r}

set.seed(34903490)
x = rnorm(50)
y = 0.5*x^2 + 2*x + rnorm(length(x))
frm = data.frame(x=x,y=y,yC=y>=as.numeric(quantile(y,probs=0.8)))
frm$absY <- abs(frm$y)
frm$posY = frm$y > 0
frm$costX = 1
WVPlots::BinaryYScatterPlot(frm, "x", "posY",
title="Example 'Probability of Y' Plot")
```


ClevelandDotPlot Plot a Cleveland dot plot.

#### Description

Plot counts of a categorical variable.
 
#### Usage
<pre><code>

ClevelandDotPlot(frm, xvar, title, ..., sort = -1, limit_n = NULL,
stem = TRUE)


</code></pre> 
#### Arguments

* ``frm``: data frame to get values from
* ``xvar ``:  name of the independent (input or model) column in frame
* ``title ``:    title to place on plot
* ``... `` : no unnamed argument, added to force named binding of later arguments
* ``sort`` : if TRUE sort data
* ``limit_n`` : if not NULL number of items to plot
* ``stem`` : if TRUE add stems/whiskers to plot

#### Details

Assumes that xvar is a factor or can be coerced to one (character or integral).
* sort < 0 sorts the factor levels in decreasing order (most frequent level first)
* sort > 0 sorts the factor levels in increasing order (good when used in conjunction with coord_
flip())
* sort = 0 leaves the factor levels in "natural order" - usually alphabetical
* stem = FALSE will plot only the dots, without the stem to the y=0 line.
* limit_n = NULL plots all the levels, N an integer limits to the top N most populous levels
 
#### Examples
```{r}

set.seed(34903490)
# discrete variable: letters of the alphabet
# frequencies of letters in English
# source: http://en.algoritmy.net/article/40379/Letter-frequency-English
letterFreqs = c(8.167, 1.492, 2.782, 4.253, 12.702, 2.228,
2.015, 6.094, 6.966, 0.153, 0.772, 4.025, 2.406, 6.749, 7.507, 1.929,
0.095, 5.987, 6.327, 9.056, 2.758, 0.978, 2.360, 0.150, 1.974, 0.074)
letterFreqs = letterFreqs/100
letterFrame = data.frame(letter = letters, freq=letterFreqs)
# now let's generate letters according to their letter frequencies
N = 1000
randomDraws = data.frame(draw=1:N,
letter=sample(letterFrame$letter, size=N,
replace=TRUE, prob=letterFrame$freq))
WVPlots::ClevelandDotPlot(randomDraws, "letter",
title = "Example Cleveland-style dot plot")
# Note the use of sort = 0, and that the graph correctly includes counts
# with no occurrences (5, and 7)
WVPlots::ClevelandDotPlot(mtcars, "carb", sort = 0, "Example of counting integer values")
```

ConditionalSmoothedScatterPlot
Plot a scatter plot with smoothing line.

#### Description

Plot a scatter plot with a smoothing line; the smoothing window is aligned either left, center or
right.
 
#### Usage
<pre><code>

ConditionalSmoothedScatterPlot(frame, xvar, yvar, groupvar, title, ...,
k = 3, align = "center")

</code></pre> 
#### Arguments

* ``frame``: data frame to get values from
* ``xvar ``:  name of the independent column in frame. Assumed to be regularly spaced
* ``yvar``:   name of the dependent (output or result to be modeled) column in frame
groupvar name of the grouping column in frame. Can be NULL for an unconditional plot
* ``title ``:    title for plot
* ``... `` : no unnamed argument, added to force named binding of later 
</code></pre> 
#### Arguments
.
k width of smoothing window. Must be odd for a center-aligned plot. Defaults to
3
align smoothing window alignment: 'center', 'left', or 'right'. Defaults to 'center'

#### Details

xvar is the continuous independent variable and yvar is the dependent binary variable. Smoothing
is by a square window of width k.
 
#### Examples
```{r}

y = c(1,2,3,4,5,10,15,18,20,25)
x = seq_len(length(y))
df = data.frame(x=x, y=y, group=x>5)
WVPlots::ConditionalSmoothedScatterPlot(df, "x", "y", NULL,
title="left smooth, one groups", align="left")
WVPlots::ConditionalSmoothedScatterPlot(df, "x", "y", "group",
title="left smooth, two groups", align="left")
6 DoubleDensityPlot
DiscreteDistribution Plot distribution of a single discrete numerical variable.

#### Description

Similar to calling ClevelandDotPlot with sort = 0 on a numerical x variable that takes on a
discrete set of values.
 
#### Usage
<pre><code>

DiscreteDistribution(frm, xvar, title, ..., stem = TRUE)

</code></pre> 
#### Arguments

* ``frm``: data frame to get values from
xvar numeric: name of the variable whose distribution is to be plotted
* ``title ``:    title to place on plot
* ``... `` : no unnamed argument, added to force named binding of later 
</code></pre> 
#### Arguments
.
stem if TRUE add whisker/stems to plot
 
#### Examples
```{r}

frmx = data.frame(x = rbinom(1000, 20, 0.5))
WVPlots::DiscreteDistribution(frmx, "x","Discrete example")
DoubleDensityPlot Plot two density plots conditioned on an outcome variable.

#### Description

Plot two density plots conditioned on a binary outcome variable.
 
#### Usage
<pre><code>

DoubleDensityPlot(frame, xvar, truthVar, title, ...)

</code></pre> 
#### Arguments

* ``frame``: data frame to get values from
* ``xvar ``:  name of the independent (input or model) column in frame
truthVar name of the dependent (output or result to be modeled) column in frame
* ``title ``:    title to place on plot
* ``... `` : no unnamed argument, added to force named binding of later 
</code></pre> 
#### Arguments
.
DoubleHistogramPlot 7

#### Details

The use case for this visualization is to plot the distribution of a predictive model score (usually the
predicted probability of a desired outcome) conditioned on the actual outcome. However, you can
use it to compare the distribution of any numerical quantity conditioned on a binary feature. See
the  
#### Examples
```{r}
.
The plot will degrade gracefully in degenerate conditions, for example when only one category is
present.
 
#### Examples
```{r}

mpg = ggplot2::mpg
mpg$trans = gsub("\\(.*$", '', mpg$trans)
WVPlots::DoubleDensityPlot(mpg, "cty", "trans", "City driving mpg by transmission type")
set.seed(34903490)
x = rnorm(50)
y = 0.5*x^2 + 2*x + rnorm(length(x))
frm = data.frame(score=x,
truth=(y>=as.numeric(quantile(y,probs=0.8))),
stuck=TRUE,
rare=FALSE)
frm[1,'rare'] = TRUE
WVPlots::DoubleDensityPlot(frm, "score", "truth", title="Example double density plot")
WVPlots::DoubleDensityPlot(frm, "score", "stuck", title="Example double density plot")
WVPlots::DoubleDensityPlot(frm, "score", "rare", title="Example double density plot")
DoubleHistogramPlot Plot two histograms conditioned on an outcome variable.

#### Description

Plot two histograms conditioned on a binary outcome variable.
 
#### Usage
<pre><code>

DoubleHistogramPlot(frame, xvar, truthVar, title, ..., breaks = 40)

</code></pre> 
#### Arguments

* ``frame``: data frame to get values from
* ``xvar ``:  name of the independent (input or model) column in frame
truthVar name of the dependent (output or result to be modeled) column in frame
* ``title ``:    title to place on plot
* ``... `` : no unnamed argument, added to force named binding of later 
</code></pre> 
#### Arguments
.
breaks breaks to pass to histogram
8 GainCurvePlot

#### Details

To distinguish the two conditions, one histogram is plotted upside-down.
The use case for this visualization is to plot a predictive model score (usually the predicted probability
of a desired outcome) conditioned on the actual outcome. However, you can use it to compare
any numerical quantity conditioned on a binary feature.
 
#### Examples
```{r}

set.seed(34903490)
x = rnorm(50)
y = 0.5*x^2 + 2*x + rnorm(length(x))
frm = data.frame(x=x,y=y,yC=y>=as.numeric(quantile(y,probs=0.8)))
frm$absY <- abs(frm$y)
frm$posY = frm$y > 0
frm$costX = 1
WVPlots::DoubleHistogramPlot(frm, "x", "yC", title="Example double histogram plot")
GainCurvePlot Plot the cumulative gain curve of a sort-order.

#### Description

Plot the cumulative gain curve of a sort-order.
 
#### Usage
<pre><code>

GainCurvePlot(frame, xvar, truthVar, title, ..., estimate_sig = FALSE,
large_count = 1000)

</code></pre> 
#### Arguments

* ``frame``: data frame to get values from
* ``xvar ``:  name of the independent (input or model score) column in frame
truthVar name of the dependent (output or result to be modeled) column in frame
* ``title ``:    title to place on plot
* ``... `` : no unnamed argument, added to force named binding of later 
</code></pre> 
#### Arguments
.
* ``estimate_sig``: (logical), if TRUE compute significance.
large_count numeric, upper bound target for number of plotting points
GainCurvePlotC 9

#### Details

The use case for this visualization is to compare a predictive model score to an actual outcome
(either binary (0/1) or continuous). In this case the gain curve plot measures how well the model
score sorts the data compared to the true outcome value.
The x-axis represents the fraction of items seen when sorted by score, and the y-axis represents the
cumulative summed true outcome represented by the items seen so far. See, for example, https://
www.ibm.com/support/knowledgecenter/SSLVMB_24.0.0/spss/tutorials/mlp_bankloan_outputtype_
02.html.
For comparison, GainCurvePlot also plots the "wizard curve": the gain curve when the data is
sorted according to its true outcome.
To improve presentation quality, the plot is limited to approximately large_count points (default:
1000). For larger data sets, the data is appropriately randomly sampled down before plotting.
 
#### Examples
```{r}

set.seed(34903490)
y = abs(rnorm(20)) + 0.1
x = abs(y + 0.5*rnorm(20))
frm = data.frame(model=x, value=y)
WVPlots::GainCurvePlot(frm, "model", "value",
title="Example Continuous Gain Curve")









PlotDistHistBeta Plot distribution 
#### Details
 as a histogram plus matching beta

#### Description

Compares empirical data to a beta distribution with the same mean and standard deviation.
 
#### Usage
<pre><code>

PlotDistHistBeta(frm, xvar, title, ..., binwidth = NULL, bins = 30)
18 plotlyROC

</code></pre> 
#### Arguments

* ``frm``: data frame to get values from
* ``xvar ``:  name of the independent (input or model) column in frame
* ``title ``:    title to place on plot
... force later 
</code></pre> 
#### Arguments
 to bind by name
binwidth passed to geom_histogram(). If passed in, overrides bins.
bins passed to geom_histogram(). Default: 30

#### Details

Plots the histogram of the empirical distribution and the density of the matching beta distribution.
Also plots the mean and plus/minus one standard deviation.
The number of bins for the histogram defaults to 30. The binwidth can also be passed in instead of
the number of bins.
Value
ggplot2 plot
 
#### Examples
```{r}

set.seed(52523)
d <- data.frame(wt=rbeta(100,shape1=0.5,shape2=0.5))
PlotDistHistBeta(d,'wt','example')



plot_Keras_fit_trajectory
Plot the trajectory of a Keras model fit.

#### Description

Plot a history of model fit performance over the number of training epochs.
 
#### Usage
<pre><code>

plot_Keras_fit_trajectory(d, title, ..., epoch_name = "epoch",
lossname = "loss", loss_pretty_name = "minus binary cross entropy",
perfname = "acc", perf_pretty_name = "accuracy",
pick_metric = loss_pretty_name, fliploss = TRUE,
discount_rate = NULL, draw_ribbon = FALSE)

</code></pre> 
#### Arguments

d data frame to get values from.
title character title for plot.
... force latera rguments  to be bound by name
epoch_name name for epoch or trajectory column.
lossname name of training loss column (default 'loss')
loss_pretty_name
name for loss on graph (default 'minus binary cross entropy')
perfname name of training performance column (default 'acc')
perf_pretty_name
name for performance metric on graph (default 'accuracy')
pick_metric character: metric to maximize (NULL for no pick line - default loss_pretty_name)
fliploss flip the loss so that "larger is better"? (default TRUE)
discount_rate numeric: what fraction of over-fit to subtract from validation performance.
draw_ribbon present the difference in training and validation performance as a ribbon rather
than two curves? (default FALSE)
22 PRPlot

#### Details

Assumes a performance matrix that carries information for both training and validation loss, and
an additional training and validation performance metric, in the format that a Keras history object
returns.
By default, flips the loss so that better performance is larger for both the loss and the performance
metric, and then draws a vertical line at the minimum validation loss (maximum flipped validation
loss). If you choose not to flip the loss, you should not use the loss as the pick_metric.
The example below gives a fit plot for a history report from Keras R package. Please see http:
//winvector.github.io/FluidData/PlotExample/KerasPerfPlot.html for some 
#### Details
.
Value
ggplot2 plot
See Also
plot_fit_trajectory
 
#### Examples
```{r}

# example data (from Keras)
d <- data.frame(
val_loss = c(0.3769818, 0.2996994, 0.2963943, 0.2779052, 0.2842501),
val_acc = c(0.8722000, 0.8895000, 0.8822000, 0.8899000, 0.8861000),
loss = c(0.5067290, 0.3002033, 0.2165675, 0.1738829, 0.1410933),
acc = c(0.7852000, 0.9040000, 0.9303333, 0.9428000, 0.9545333) )
plt <- plot_Keras_fit_trajectory(
d,
title = "model performance by epoch, dataset, and measure")
suppressWarnings(print(plt)) # too few points for loess
PRPlot Plot Precision-Recall plot.

#### Description

Plot Precision-Recall plot.
 
#### Usage
<pre><code>

PRPlot(frame, xvar, truthVar, truthTarget, title, ...,
estimate_sig = FALSE)
ROCPlot 23

</code></pre> 
#### Arguments

* ``frame``: data frame to get values from
* ``xvar ``:  name of the independent (input or model) column in frame
truthVar name of the dependent (output or result to be modeled) column in frame
truthTarget value we consider to be positive
* ``title ``:    title to place on plot
* ``... `` : no unnamed argument, added to force named binding of later 
</code></pre> 
#### Arguments
.
* ``estimate_sig``: (logical), if TRUE compute significance

#### Details

See http://www.nature.com/nmeth/journal/v13/n8/full/nmeth.3945.html for a discussion of precision
and recall, and how the precision/recall plot relates to the ROC plot.
In addition to plotting precision versus recall, PRPlot reports the best achieved F1 score, and plots
an isoline corresponding to that F1 score.
See Also
ROCPlot
 
#### Examples
```{r}

set.seed(34903490)
x = rnorm(50)
y = 0.5*x^2 + 2*x + rnorm(length(x))
frm = data.frame(x=x,y=y,yC=y>=as.numeric(quantile(y,probs=0.8)))
frm$absY <- abs(frm$y)
frm$posY = frm$y > 0
frm$costX = 1
WVPlots::PRPlot(frm, "x", "yC", TRUE, title="Example Precision-Recall plot")
ROCPlot Plot receiver operating characteristic plot.

#### Description

Plot receiver operating characteristic plot.
 
#### Usage
<pre><code>

ROCPlot(frame, xvar, truthVar, truthTarget, title, ...,
estimate_sig = FALSE, returnScores = FALSE, nrep = 100,
parallelCluster = NULL)
24 ROCPlotPair

</code></pre> 
#### Arguments

* ``frame``: data frame to get values from
* ``xvar ``:  name of the independent (input or model) column in frame
truthVar name of the dependent (output or result to be modeled) column in frame
truthTarget value we consider to be positive
* ``title ``:    title to place on plot
* ``... `` : no unnamed argument, added to force named binding of later 
</code></pre> 
#### Arguments
.
* ``estimate_sig``: (logical), if TRUE estimate and display significance of difference from AUC 0.5.
returnScores logical if TRUE return detailed permutedScores
nrep number of permutation repetitions to estimate p values.
parallelCluster
(optional) a cluster object created by package parallel or package snow.

#### Details

See http://www.nature.com/nmeth/journal/v13/n8/full/nmeth.3945.html for a discussion of true positive
and false positive rates, and how the ROC plot relates to the precision/recall plot.
See Also
PRPlot
 
#### Examples
```{r}

set.seed(34903490)
x = rnorm(50)
y = 0.5*x^2 + 2*x + rnorm(length(x))
frm = data.frame(x=x,yC=y>=as.numeric(quantile(y,probs=0.8)))
WVPlots::ROCPlot(frm, "x", "yC", TRUE, title="Example ROC plot", estimate_sig = TRUE)
ROCPlotPair Compare two ROC plots.

#### Description

Plot two receiver operating characteristic curves from the same data.frame.
 
#### Usage
<pre><code>

ROCPlotPair(frame, xvar1, xvar2, truthVar, truthTarget, title, ...,
estimate_sig = FALSE, returnScores = FALSE, nrep = 100,
parallelCluster = NULL)
ROCPlotPair2 25

</code></pre> 
#### Arguments

* ``frame``: data frame to get values from
xvar1 name of the first independent (input or model) column in frame
xvar2 name of the second independent (input or model) column in frame
truthVar name of the dependent (output or result to be modeled) column in frame
truthTarget value we consider to be positive
* ``title ``:    title to place on plot
* ``... `` : no unnamed argument, added to force named binding of later 
</code></pre> 
#### Arguments
.
* ``estimate_sig``: (logical), if TRUE estimate and display significance of difference from AUC 0.5.
returnScores logical if TRUE return detailed permutedScores
nrep number of permutation repetitions to estimate p values.
parallelCluster
(optional) a cluster object created by package parallel or package snow.

#### Details

The use case for this function is to compare the performance of two models when applied to a data
set, where the predictions from both models are columns of the same data frame.
See Also
ROCPlot
 
#### Examples
```{r}

set.seed(34903490)
x1 = rnorm(50)
x2 = rnorm(length(x1))
y = 0.2*x2^2 + 0.5*x2 + x1 + rnorm(length(x1))
frm = data.frame(x1=x1,x2=x2,yC=y>=as.numeric(quantile(y,probs=0.8)))
# WVPlots::ROCPlot(frm, "x1", "yC", TRUE, title="Example ROC plot")
# WVPlots::ROCPlot(frm, "x2", "yC", TRUE, title="Example ROC plot")
WVPlots::ROCPlotPair(frm, "x1", "x2", "yC", TRUE,
title="Example ROC pair plot", estimate_sig = TRUE)
ROCPlotPair2 Compare two ROC plots.

#### Description

Plot two receiver operating characteristic curves from different data frames.
26 ROCPlotPair2
 
#### Usage
<pre><code>

ROCPlotPair2(nm1, frame1, xvar1, truthVar1, truthTarget1, nm2, frame2,
xvar2, truthVar2, truthTarget2, title, ..., estimate_sig = TRUE,
returnScores = FALSE, nrep = 100, parallelCluster = NULL)

</code></pre> 
#### Arguments

nm1 name of first model
frame1 data frame to get values from
xvar1 name of the first independent (input or model) column in frame
truthVar1 name of the dependent (output or result to be modeled) column in frame
truthTarget1 value we consider to be positive
nm2 name of second model
frame2 data frame to get values from
xvar2 name of the first independent (input or model) column in frame
truthVar2 name of the dependent (output or result to be modeled) column in frame
truthTarget2 value we consider to be positive
* ``title ``:    title to place on plot
* ``... `` : no unnamed argument, added to force named binding of later 
</code></pre> 
#### Arguments
.
* ``estimate_sig``: (logical), if TRUE estimate and display significance of difference from AUC 0.5.
returnScores logical if TRUE return detailed permutedScores
nrep number of permutation repetitions to estimate p values.
parallelCluster
(optional) a cluster object created by package parallel or package snow.

#### Details

Use this curve to compare model predictions to true outcome from two data frames, each of which
has its own model predictions and true outcome columns.
See Also
ROCPlot
 
#### Examples
```{r}

set.seed(34903490)
x1 = rnorm(50)
x2 = rnorm(length(x1))
y = 0.2*x2^2 + 0.5*x2 + x1 + rnorm(length(x1))
frm = data.frame(x1=x1,x2=x2,yC=y>=as.numeric(quantile(y,probs=0.8)))
# WVPlots::ROCPlot(frm, "x1", "yC", TRUE, title="Example ROC plot")
# WVPlots::ROCPlot(frm, "x2", "yC", TRUE, title="Example ROC plot")
WVPlots::ROCPlotPair2('train',frm, "x1", "yC", TRUE,
ScatterBoxPlot 27
'test', frm, "x2", "yC", TRUE,
title="Example ROC pair plot", estimate_sig = TRUE)



28 ScatterBoxPlotH
ScatterBoxPlotH Plot a scatter box plot in horizontal mode.

#### Description

Plot a boxplot with the data points superimposed. Box plots are aligned horizontally.
 
#### Usage
<pre><code>

ScatterBoxPlotH(frm, xvar, yvar, title, ..., pt_alpha = 0.3)

</code></pre> 
#### Arguments

* ``frm``: data frame to get values from
* ``xvar ``:  name of the continuous column in frame
* ``yvar``:   name of the independent column in frame; assumed discrete
title plot title
... (doesn't take additional 
</code></pre> 
#### Arguments
, used to force later arguments
 by name)
pt_alpha transparency of points in scatter plot

#### Details

xvar is a continuous variable and yvar is a discrete variable. If frm[[yvar]] is an integer column,
it will be converted to a factor. This means that additional layers that rely on continuous y scales
won't work.
See Also
ScatterBoxPlot
 
#### Examples
```{r}

classes = c("a", "b", "c")
means = c(2, 4, 3)
names(means) = classes
label = sample(classes, size=1000, replace=TRUE)
meas = means[label] + rnorm(1000)
frm2 = data.frame(label=label,
meas = meas)
WVPlots::ScatterBoxPlotH(frm2, "meas", "label", pt_alpha=0.2, title="Example Scatter/Box plot")

```
WVPlots WVPlots: Common Plots for Analysis

#### Description

Select data analysis plots, under a standardized calling interface implemented on top of ggplot2
and plotly. Plots of interest include: ROC, gain curve, scatter plot with marginal distributions, conditioned
scatter plot with marginal densities. box and stem with matching theoretical distribution,
density with matching theoretical distribution.

#### Details

For more information:
* vignette(package='WVPlots')
* RShowDoc('WVPlots_ 
#### Examples
```{r}
',package='WVPlots')
* Website: https://github.com/WinVector/WVPlots
Index
BinaryYScatterPlot, 2
ClevelandDotPlot, 3
ConditionalSmoothedScatterPlot, 5
DiscreteDistribution, 6
DoubleDensityPlot, 6
DoubleHistogramPlot, 7
GainCurvePlot, 8, 10, 11
GainCurvePlotC, 9
GainCurvePlotWithNotation, 10
geom_hex, 12
geom_histogram, 35
HexBinPlot, 11
LiftCurvePlot, 12
LogLogPlot, 13
PairPlot, 14
plot_fit_trajectory, 19, 22
plot_Keras_fit_trajectory, 20, 21
PlotDistCountNormal, 15
PlotDistDensityBeta, 16
PlotDistDensityNormal, 17
PlotDistHistBeta, 17
plotlyROC, 18
PRPlot, 22, 24
ROCPlot, 19, 23, 23, 25, 26
ROCPlotPair, 24
ROCPlotPair2, 25
scale_fill_manual, 35
ScatterBoxPlot, 27, 28
ScatterBoxPlotH, 27, 28
ScatterHist, 29, 31
ScatterHistC, 30, 30, 32
ScatterHistN, 31
ShadedDensity, 32, 34
ShadedDensityCenter, 33, 33
ShadowHist, 34
ShadowPlot, 35
WVPlots, 36
WVPlots-package (WVPlots), 36
37