Package 'ggRandomForests'
September 7, 2016
Type Package
Title Visually Exploring Random Forests
Version 2.0.1
Date 2016-09-07
Author John Ehrlinger <john.ehrlinger@gmail.com>
Maintainer John Ehrlinger <john.ehrlinger@gmail.com>
License GPL (>= 3)
URL https://github.com/ehrlinger/ggRandomForests
BugReports https://github.com/ehrlinger/ggRandomForests/issues
#### Description 
 Graphic elements for exploring Random Forests using the 'randomForest' or
'randomForestSRC' package for survival, regression and classification forests and
'ggplot2' package plotting.
Depends R (>= 3.1.0), randomForestSRC (>= 1.5.5)
Imports randomForest, ggplot2, survival, parallel, tidyr
Suggests testthat, rmdformats, RColorBrewer, MASS, dplyr, knitr,
rmarkdown, plot3D
RoxygenNote 5.0.1
NeedsCompilation no
Repository CRAN
Date/Publication 2016-09-07 23:21:30
R topics documented:
ggRandomForests-package . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 2
cache_rfsrc_datasets . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 4
calc_auc . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 5
calc_roc.rfsrc . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 6
combine.gg_partial . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 7
gg_error . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 8
gg_interaction . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 10
1
2 ggRandomForests-package
gg_minimal_depth . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 13
gg_minimal_vimp . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 15
gg_partial . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 17
gg_partial_coplot.rfsrc . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 20
gg_rfsrc.rfsrc . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 22
gg_roc.rfsrc . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 24
gg_survival . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 25
gg_variable . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 26
gg_vimp . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 29
kaplan . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 30
logit_loess . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 32
nelson . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 32
partial.rfsrc . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 33
plot.gg_error . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 36
plot.gg_interaction . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 38
plot.gg_minimal_depth . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 40
plot.gg_minimal_vimp . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 43
plot.gg_partial . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 45
plot.gg_partial_list . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 48
plot.gg_rfsrc . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 50
plot.gg_roc . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 52
plot.gg_survival . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 54
plot.gg_variable . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 55
plot.gg_vimp . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 57
print.gg_minimal_depth . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 59
quantile_pts . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 60
shift . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 61
surface_matrix . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 62
Index 64
ggRandomForests-package
ggRandomForests: Visually Exploring Random Forests
#### Description 

ggRandomForests is a utility package for randomForestSRC (Iswaran et.al. 2014, 2008, 2007) for
survival, regression and classification forests and uses the ggplot2 (Wickham 2009) package for
plotting results. ggRandomForests is structured to extract data objects from the random forest and
provides S3 functions for printing and plotting these objects.
The randomForestSRC package provides a unified treatment of Breiman's (2001) random forests
for a variety of data settings. Regression and classification forests are grown when the response
is numeric or categorical (factor) while survival and competing risk forests (Ishwaran et al. 2008,
2012) are grown for right-censored survival data.
Many of the figures created by the ggRandomForests package are also available directly from
within the randomForestSRC package. However, ggRandomForests offers the following advantages:
ggRandomForests-package 3
*  Separation of data and figures: ggRandomForest contains functions that operate on either
the rfsrc forest object directly, or on the output from randomForestSRC post processing
functions (i.e. plot.variable, var.select, find.interaction) to generate intermediate
ggRandomForests data objects. S3 functions are provide to further process these objects
and plot results using the ggplot2 graphics package. Alternatively, users can use these data
objects for additional custom plotting or analysis operations.
*  Each data object/figure is a single, self contained object. This allows simple modification and
manipulation of the data or ggplot2 objects to meet users specific needs and requirements.
*  The use of ggplot2 for plotting. We chose to use the ggplot2 package for our figures to
allow users flexibility in modifying the figures to their liking. Each S3 plot function returns
either a single ggplot2 object, or a list of ggplot2 objects, allowing users to use additional
ggplot2 functions or themes to modify and customise the figures to their liking.
The ggRandomForests package contains the following data functions:
*  gg_rfsrc: randomForest[SRC] predictions.
*  gg_error: randomForest[SRC] convergence rate based on the OOB error rate.
*  gg_roc: ROC curves for randomForest classification models.
*  gg_vimp: Variable Importance ranking for variable selection.
*  gg_minimal_depth: Minimal Depth ranking for variable selection (Ishwaran et.al. 2010).
*  gg_minimal_vimp: Comparing Minimal Depth and VIMP rankings for variable selection.
*  gg_interaction: Minimal Depth interaction detection (Ishwaran et.al. 2010)
*  gg_variable: Marginal variable dependence.
*  gg_partial: Partial (risk adjusted) variable dependence.
*  gg_partial_coplot: Partial variable conditional dependence (computationally expensive).
*  gg_survival: Kaplan-Meier/Nelson-Aalon hazard analysis.
Each of these data functions has an associated S3 plot function that returns ggplot2 objects, either
individually or as a list, which can be further customised using standard ggplot2 commands.

4 cache_rfsrc_datasets
cache_rfsrc_datasets Recreate the cached data sets for the ggRandomForests package
#### Description 

Recreate the cached data sets for the ggRandomForests package
#### Usage 
<pre><code>

cache_rfsrc_datasets(set = NA, save = TRUE, pth, ...)

</code></pre>
#### Arguments

set Defaults to all sets (NA), however for individual sets specify one or more of
c("airq", "Boston", "iris", "mtcars", "pbc", "veteran")
save Defaults to write files to the current data directory.
pth the directory to store files.
... extra 
</code></pre>
#### Arguments
 passed to randomForestSRC functions.
Details
Constructing random forests are computationally expensive, and the ggRandomForests operates
directly on randomForestSRC objects. We cache computationally intensive randomForestSRC objects
to improve the ggRandomForests #### Examples 
```{r} 
, diagnostics and vignettes run times. The set of
precompiled randomForestSRC objects are stored in the package data subfolder, however version
changes in the dependant packages may break some functionality. This function was created to help
the package developer deal with thoses changes. We make the function available to end users to
create objects for further experimentation.
For the following data sets: #'
*  _iris - The iris data set.
*  _airq - The airquality data set.
*  _mtcars - The mtcars data set.
*  _Boston - The Boston housing data set (MASS package).
*  _pbc - The pbc data set (randomForestSRC package).
*  _veteran - The veteran data set (randomForestSRC package).
See Also
iris airq mtcars Boston pbc veteran
calc_auc 5
calc_auc Area Under the ROC Curve calculator
#### Description 

Area Under the ROC Curve calculator
#### Usage 
<pre><code>

calc_auc(x)

</code></pre>
#### Arguments

x gg_roc object
Details
calc_auc uses the trapezoidal rule to calculate the area under the ROC curve.
This is a helper function for the gg_roc functions.
Value
AUC. 50% is random guessing, higher is better.
See Also
calc_roc gg_roc plot.gg_roc
#### Examples 
```{r} 

##
## Taken from the gg_roc example
rfsrc_iris <- rfsrc(Species ~ ., data = iris)
#data(rfsrc_iris)
## Not run:
gg_dta <- gg_roc(rfsrc_iris, which.outcome=1)
calc_auc(gg_dta)
## End(Not run)
gg_dta <- gg_roc(rfsrc_iris, which.outcome=2)
calc_auc(gg_dta)
6 calc_roc.rfsrc
calc_roc.rfsrc Reciever Operator Characteristic calculator
#### Description 

Reciever Operator Characteristic calculator
#### Usage 
<pre><code>

calc_roc.rfsrc(object, yvar, which.outcome = "all", oob = TRUE)

</code></pre>
#### Arguments

object rfsrc or predict.rfsrc object containing predicted response
yvar True response variable
which.outcome If defined, only show ROC for this response.
oob Use OOB estimates, the normal validation method (TRUE)
Details
For a randomForestSRC prediction and the actual response value, calculate the specificity (1-False
Positive Rate) and sensitivity (True Positive Rate) of a predictor.
This is a helper function for the gg_roc functions, and not intended for use by the end user.
Value
A gg_roc object
See Also
calc_auc gg_roc plot.gg_roc
#### Examples 
```{r} 

## Taken from the gg_roc example
rfsrc_iris <- rfsrc(Species ~ ., data = iris)
#data(rfsrc_iris)
gg_dta <- calc_roc.rfsrc(rfsrc_iris, rfsrc_iris$yvar, which.outcome=1, oob=TRUE)
gg_dta <- calc_roc.rfsrc(rfsrc_iris, rfsrc_iris$yvar, which.outcome=1, oob=FALSE)
combine.gg_partial 7
combine.gg_partial combine two gg_partial objects
#### Description 

The combine.gg_partial function assumes the two gg_partial objects were generated from the
same rfsrc object. So, the function joins along the gg_partial list item names (one per partial
plot variable). Further, we combine the two gg_partial objects along the group variable.
Hence, to join three gg_partial objects together (i.e. for three different time points from a survival
random forest) would require two combine.gg_partial calls: One to join the first two gg_partial
object, and one to append the third gg_partial object to the output from the first call. The second
call will append a single lbls label to the gg_partial object.
#### Usage 
<pre><code>

combine.gg_partial(x, y, lbls, ...)

</code></pre>
#### Arguments

x gg_partial object
y gg_partial object
lbls vector of 2 strings to label the combined data.
... not used
Value
gg_partial or gg_partial_list based on class of x and y.
#### Examples 
```{r} 

## Not run:
# Load a set of plot.variable partial plot data
data(partial_pbc)
# A list of 2 plot.variable objects
length(partial_pbc)
class(partial_pbc)
class(partial_pbc[[1]])
class(partial_pbc[[2]])
# Create gg_partial objects
ggPrtl.1 <- gg_partial(partial_pbc[[1]])
ggPrtl.2 <- gg_partial(partial_pbc[[2]])
# Combine the objects to get multiple time curves
# along variables on a single figure.
ggpart <- combine.gg_partial(ggPrtl.1, ggPrtl.2,
8 gg_error
lbls = c("1 year", "3 years"))
# Plot each figure separately
plot(ggpart)
# Get the continuous data for a panel of continuous plots.
ggcont <- ggpart
ggcont$edema <- ggcont$ascites <- ggcont$stage <- NULL
plot(ggcont, panel=TRUE)
# And the categorical for a panel of categorical plots.
nms <- colnames(sapply(ggcont, function(st){st}))
for(ind in nms){
ggpart[[ind]] <- NULL
}
plot(ggpart, panel=TRUE)
## End(Not run)
gg_error randomForestSRC error rate data object
#### Description 

Extract the cumulative (OOB) randomForestSRC error rate as a function of number of trees.
#### Usage 
<pre><code>

gg_error(object, ...)

</code></pre>
#### Arguments

object rfsrc object.
... optional arguments (not used).
Details
The gg_error function simply returns the rfsrc$err.rate object as a data.frame, and assigns the
class for connecting to the S3 plot.gg_error function.
Value
gg_error data.frame with one column indicating the tree number, and the remaining columns
from the rfsrc$err.rate return value.
gg_error 9


See Also
plot.gg_error rfsrc plot.rfsrc
#### Examples 
```{r} 

## #### Examples 
```{r} 
 from RFSRC package...
## ------------------------------------------------------------
## classification example
## ------------------------------------------------------------
## ------------- iris data
## You can build a randomForest
rfsrc_iris <- rfsrc(Species ~ ., data = iris)
# ... or load a cached randomForestSRC object
# data(rfsrc_iris, package="ggRandomForests")
# Get a data.frame containing error rates
gg_dta<- gg_error(rfsrc_iris)
# Plot the gg_error object
plot(gg_dta)
## ------------------------------------------------------------
## Regression example
## ------------------------------------------------------------
## Not run:
## ------------- airq data
rfsrc_airq <- rfsrc(Ozone ~ ., data = airquality, na.action = "na.impute")
# Get a data.frame containing error rates
gg_dta<- gg_error(rfsrc_airq)
# Plot the gg_error object
plot(gg_dta)
## End(Not run)
## Not run:
## ------------- Boston data
data(rfsrc_Boston, package="ggRandomForests")
# Get a data.frame containing error rates
gg_dta<- gg_error(rfsrc_Boston)
# Plot the gg_error object
plot(gg_dta)
## End(Not run)
## Not run:
## ------------- mtcars data
# Get a data.frame containing error rates
gg_dta<- gg_error(rfsrc_mtcars)
# Plot the gg_error object
plot(gg_dta)
## End(Not run)
## ------------------------------------------------------------
## Survival example
## ------------------------------------------------------------
## Not run:
## ------------- veteran data
## randomized trial of two treatment regimens for lung cancer
data(veteran, package = "randomForestSRC")
rfsrc_veteran <- rfsrc(Surv(time, status) ~ ., data = dta$veteran, ...)
gg_dta <- gg_error(rfsrc_veteran)
plot(gg_dta)
## End(Not run)
## Not run:
## ------------- pbc data
# Load a cached randomForestSRC object
data(rfsrc_pbc, package="ggRandomForests")
gg_dta <- gg_error(rfsrc_pbc)
plot(gg_dta)
## End(Not run)
gg_interaction Minimal Depth Variable Interaction data object
(find.interaction).
#### Description 

Converts the matrix returned from find.interaction to a data.frame and add attributes for S3
identification. If passed a rfsrc object, gg_interaction first runs the find.interaction function
with all optional 
</code></pre>
#### Arguments
.
#### Usage 
<pre><code>

gg_interaction(object, ...)
gg_interaction 11

</code></pre>
#### Arguments

object a rfsrc object or the output from the find.interaction function call.
... optional extra arguments
 passed to find.interaction.
Value
gg_interaction object

See Also
rfsrc find.interaction max.subtree var.select vimp plot.gg_interaction
#### Examples 
```{r} 

## #### Examples 
```{r} 
 from randomForestSRC package...
## ------------------------------------------------------------
## find interactions, classification setting
## ------------------------------------------------------------
## Not run:
## -------- iris data
## iris.obj <- rfsrc(Species ~., data = iris)
## TODO: VIMP interactions not handled yet....
## randomForestSRC::find.interaction(iris.obj, method = "vimp", nrep = 3)
## interaction_iris <- randomForestSRC::find.interaction(iris.obj)
data(interaction_iris, package="ggRandomForests")
gg_dta <- gg_interaction(interaction_iris)
plot(gg_dta, xvar="Petal.Width")
plot(gg_dta, panel=TRUE)
## End(Not run)
## ------------------------------------------------------------
## find interactions, regression setting
## ------------------------------------------------------------
## Not run:
## -------- air quality data
## airq.obj <- rfsrc(Ozone ~ ., data = airquality)
##
## TODO: VIMP interactions not handled yet....
## randomForestSRC::find.interaction(airq.obj, method = "vimp", nrep = 3)
## interaction_airq <- randomForestSRC::find.interaction(airq.obj)

data(interaction_airq, package="ggRandomForests")
gg_dta <- gg_interaction(interaction_airq)
plot(gg_dta, xvar="Temp")
plot(gg_dta, xvar="Solar.R")
plot(gg_dta, panel=TRUE)
## End(Not run)
## Not run:
## -------- Boston data
data(interaction_Boston, package="ggRandomForests")
gg_dta <- gg_interaction(interaction_Boston)
plot(gg_dta, panel=TRUE)
## End(Not run)
## Not run:
## -------- mtcars data
data(interaction_mtcars, package="ggRandomForests")
gg_dta <- gg_interaction(interaction_mtcars)
plot(gg_dta, panel=TRUE)
## End(Not run)
## ------------------------------------------------------------
## find interactions, survival setting
## ------------------------------------------------------------
## -------- pbc data
## data(pbc, package = "randomForestSRC")
## pbc.obj <- rfsrc(Surv(days,status) ~ ., pbc, nsplit = 10)
## interaction_pbc <- randomForestSRC::find.interaction(pbc.obj, nvar = 8)
## Not run:
data(interaction_pbc, package="ggRandomForests")
gg_dta <- gg_interaction(interaction_pbc)
plot(gg_dta, xvar="bili")
plot(gg_dta, panel=TRUE)
## End(Not run)
## Not run:
## -------- veteran data
data(interaction_veteran, package="ggRandomForests")
gg_dta <- gg_interaction(interaction_veteran)
plot(gg_dta, panel=TRUE)
## End(Not run)
gg_minimal_depth 13
gg_minimal_depth Minimal depth data object ([randomForestSRC]{var.select})
#### Description 

the [randomForestSRC]{var.select} function implements random forest variable selection using
tree minimal depth methodology. The gg_minimal_depth function takes the output from
[randomForestSRC]{var.select} and creates a data.frame formatted for the plot.gg_minimal_depth
function.
#### Usage 
<pre><code>

gg_minimal_depth(object, ...)

</code></pre>
#### Arguments

object A [randomForestSRC]{rfsrc} object, [randomForestSRC]{predict} object
or the list from the [randomForestSRC]{var.select.rfsrc} function.
... optional arguments
 passed to the [randomForestSRC]{var.select} function
if operating on an [randomForestSRC]{rfsrc} object.
Value
gg_minimal_depth object, A modified list of variables from the [randomForestSRC]{var.select}
function, ordered by minimal depth rank.
See Also
[randomForestSRC]{var.select} plot.gg_minimal_depth
#### Examples 
```{r} 

## #### Examples 
```{r} 
 from RFSRC package...
## ------------------------------------------------------------
## classification example
## ------------------------------------------------------------
## Not run:
## -------- iris data
## You can build a randomForest
# rfsrc_iris <- rfsrc(Species ~ ., data = iris)
# varsel_iris <- randomForestSRC::var.select(rfsrc_iris)
# ... or load a cached randomForestSRC object
data(varsel_iris, package="ggRandomForests")
# Get a data.frame containing minimaldepth measures
gg_dta<- gg_minimal_depth(varsel_iris)
# Plot the gg_minimal_depth object
plot(gg_dta)
## End(Not run)
## ------------------------------------------------------------
## Regression example
## ------------------------------------------------------------
## Not run:
## -------- air quality data
# rfsrc_airq <- rfsrc(Ozone ~ ., data = airquality, na.action = "na.impute")
# varsel_airq <- randomForestSRC::var.select(rfsrc_airq)
# ... or load a cached randomForestSRC object
data(varsel_airq, package="ggRandomForests")
# Get a data.frame containing error rates
gg_dta<- gg_minimal_depth(varsel_airq)
# Plot the gg_minimal_depth object
plot(gg_dta)
## End(Not run)
## Not run:
## -------- Boston data
data(varsel_Boston, package="ggRandomForests")
# Get a data.frame containing error rates
plot(gg_minimal_depth(varsel_Boston))
## End(Not run)
## Not run:
## -------- mtcars data
data(varsel_mtcars, package="ggRandomForests")
# Get a data.frame containing error rates
plot.gg_minimal_depth(varsel_mtcars)
## End(Not run)
## ------------------------------------------------------------
## Survival example
## ------------------------------------------------------------
## Not run:
## -------- veteran data
## veteran data
## randomized trial of two treatment regimens for lung cancer
# data(veteran, package = "randomForestSRC")
# rfsrc_veteran <- rfsrc(Surv(time, status) ~ ., data = veteran, ntree = 100)
# varsel_veteran <- randomForestSRC::var.select(rfsrc_veteran)
# Load a cached randomForestSRC object
data(varsel_veteran, package="ggRandomForests")
gg_dta <- gg_minimal_depth(varsel_veteran)
plot(gg_dta)
## End(Not run)
gg_minimal_vimp 15
## Not run:
## -------- pbc data
data(varsel_pbc, package="ggRandomForests")
gg_dta <- gg_minimal_depth(varsel_pbc)
plot(gg_dta)
## End(Not run)
gg_minimal_vimp Minimal depth vs VIMP camparison by variable rankings.
#### Description 

Minimal depth vs VIMP camparison by variable rankings.
#### Usage 
<pre><code>

gg_minimal_vimp(object, ...)

</code></pre>
#### Arguments

object A rfsrc object, predict.rfsrc object or the list from the var.select.rfsrc
function.
... optional arguments
 passed to the var.select function if operating on an rfsrc
object.
@return gg_minimal_vimp comparison object.
@seealso plot.gg_minimal_vimp var.select
@aliases gg_minimal_vimp
#### Examples 
```{r} 

## Examples from RFSRC package...
## ------------------------------------------------------------
## classification example
## ------------------------------------------------------------
## Not run:
## -------- iris data
## You can build a randomForest
# rfsrc_iris <- rfsrc(Species ~ ., data = iris)
# varsel_iris <- randomForestSRC::var.select(rfsrc_iris)
# ... or load a cached randomForestSRC object
data(varsel_iris, package="ggRandomForests")
# Get a data.frame containing minimaldepth measures
gg_dta<- gg_minimal_vimp(varsel_iris)
# Plot the gg_minimal_depth object
plot(gg_dta)
16 gg_minimal_vimp
## End(Not run)
## ------------------------------------------------------------
## Regression example
## ------------------------------------------------------------
## Not run:
## -------- air quality data
# rfsrc_airq <- rfsrc(Ozone ~ ., data = airquality, na.action = "na.impute")
# varsel_airq <- randomForestSRC::var.select(rfsrc_airq)
# ... or load a cached randomForestSRC object
data(varsel_airq, package="ggRandomForests")
# Get a data.frame containing error rates
gg_dta<- gg_minimal_vimp(varsel_airq)
# Plot the gg_minimal_vimp object
plot(gg_dta)
## End(Not run)
## Not run:
## -------- Boston data
data(varsel_Boston, package="ggRandomForests")
# Get a data.frame containing error rates
gg_dta<- gg_minimal_vimp(varsel_Boston)
# Plot the gg_minimal_vimp object
plot(gg_dta)
## End(Not run)
## Not run:
## -------- mtcars data
data(varsel_mtcars, package="ggRandomForests")
# Get a data.frame containing error rates
gg_dta<- gg_minimal_vimp(varsel_mtcars)
# Plot the gg_minimal_vimp object
plot(gg_dta)
## End(Not run)
## ------------------------------------------------------------
## Survival example
## ------------------------------------------------------------
## Not run:
## -------- veteran data
## randomized trial of two treatment regimens for lung cancer
# data(veteran, package = "randomForestSRC")
# rfsrc_veteran <- rfsrc(Surv(time, status) ~ ., data = veteran, ntree = 100)
# varsel_veteran <- randomForestSRC::var.select(rfsrc_veteran)
# Load a cached randomForestSRC object
data(varsel_veteran, package="ggRandomForests")
gg_partial 17
gg_dta <- gg_minimal_vimp(varsel_veteran)
plot(gg_dta)
## End(Not run)
## Not run:
## -------- pbc data
data(varsel_pbc, package="ggRandomForests")
gg_dta <- gg_minimal_vimp(varsel_pbc)
plot(gg_dta)
## End(Not run)
```


gg_partial Partial variable dependence object
#### Description 

The plot.variable function returns a list of either marginal variable dependance or partial variable
dependence data from a rfsrc object. The gg_partial function formulates the plot.variable
output for partial plots (where partial=TRUE) into a data object for creation of partial dependence
plots using the plot.gg_partial function.
Partial variable dependence plots are the risk adjusted estimates of the specified response as a function
of a single covariate, possibly subsetted on other covariates.
An option named argument can name a column for merging multiple plots together
#### Usage 
<pre><code>

gg_partial(object, ...)

</code></pre>
#### Arguments

object the partial variable dependence data object from plot.variable function
... optional 
</code></pre>
#### Arguments

Value
gg_partial object. A data.frame or list of data.frames corresponding the variables contained
within the plot.variable output.

See Also
plot.gg_partial plot.variable
18 gg_partial
#### Examples 
```{r} 

## ------------------------------------------------------------
## classification
## ------------------------------------------------------------
## -------- iris data
## Not run:
## iris "Petal.Width" partial dependence plot
##
# rfsrc_iris <- rfsrc(Species ~., data = iris)
# partial_iris <- plot.variable(rfsrc_iris, xvar.names = "Petal.Width",
# partial=TRUE)
data(partial_iris, package="ggRandomForests")
gg_dta <- gg_partial(partial_iris)
plot(gg_dta)
## End(Not run)
## ------------------------------------------------------------
## regression
## ------------------------------------------------------------
## Not run:
## -------- air quality data
## airquality "Wind" partial dependence plot
##
# rfsrc_airq <- rfsrc(Ozone ~ ., data = airquality)
# partial_airq <- plot.variable(rfsrc_airq, xvar.names = "Wind",
# partial=TRUE, show.plot=FALSE)
data(partial_airq, package="ggRandomForests")
gg_dta <- gg_partial(partial_airq)
plot(gg_dta)
gg_dta.m <- gg_dta[["Month"]]
plot(gg_dta.m, notch=TRUE)
gg_dta[["Month"]] <- NULL
plot(gg_dta, panel=TRUE)
## End(Not run)
## Not run:
## -------- Boston data
data(partial_Boston, package="ggRandomForests")
gg_dta <- gg_partial(partial_Boston)
plot(gg_dta, panel=TRUE)
## End(Not run)
## Not run:
## -------- mtcars data
data(partial_mtcars, package="ggRandomForests")
gg_dta <- gg_partial(partial_mtcars)
gg_partial 19
gg_dta.cat <- gg_dta
gg_dta.cat[["disp"]] <- gg_dta.cat[["wt"]] <- gg_dta.cat[["hp"]] <- NULL
gg_dta.cat[["drat"]] <- gg_dta.cat[["carb"]] <- gg_dta.cat[["qsec"]] <- NULL
plot(gg_dta.cat, panel=TRUE, notch=TRUE)
gg_dta[["cyl"]] <- gg_dta[["vs"]] <- gg_dta[["am"]] <- NULL
gg_dta[["gear"]] <- NULL
plot(gg_dta, panel=TRUE)
## End(Not run)
## ------------------------------------------------------------
## survival #### Examples 
```{r} 

## ------------------------------------------------------------
## Not run:
## -------- veteran data
## survival "age" partial variable dependence plot
##
# data(veteran, package = "randomForestSRC")
# rfsrc_veteran <- rfsrc(Surv(time,status)~., veteran, nsplit = 10, ntree = 100)
#
## 30 day partial plot for age
# partial_veteran <- plot.variable(rfsrc_veteran, surv.type = "surv",
# partial = TRUE, time=30,
# xvar.names = "age",
# show.plots=FALSE)
data(partial_veteran, package="ggRandomForests")
gg_dta <- gg_partial(partial_veteran[[1]])
plot(gg_dta)
gg_dta.cat <- gg_dta
gg_dta[["celltype"]] <- gg_dta[["trt"]] <- gg_dta[["prior"]] <- NULL
plot(gg_dta, panel=TRUE)
gg_dta.cat[["karno"]] <- gg_dta.cat[["diagtime"]] <- gg_dta.cat[["age"]] <- NULL
plot(gg_dta.cat, panel=TRUE, notch=TRUE)
gg_dta <- lapply(partial_veteran, gg_partial)
gg_dta <- combine.gg_partial(gg_dta[[1]], gg_dta[[2]] )
plot(gg_dta[["karno"]])
plot(gg_dta[["celltype"]])
gg_dta.cat <- gg_dta
gg_dta[["celltype"]] <- gg_dta[["trt"]] <- gg_dta[["prior"]] <- NULL
plot(gg_dta, panel=TRUE)
gg_dta.cat[["karno"]] <- gg_dta.cat[["diagtime"]] <- gg_dta.cat[["age"]] <- NULL
plot(gg_dta.cat, panel=TRUE, notch=TRUE)
## End(Not run)
20 gg_partial_coplot.rfsrc
## Not run:
## -------- pbc data
data("partial_pbc", package = "ggRandomForests")
data("varsel_pbc", package = "ggRandomForests")
xvar <- varsel_pbc$topvars
# Convert all partial plots to gg_partial objects
gg_dta <- lapply(partial_pbc, gg_partial)
# Combine the objects to get multiple time curves
# along variables on a single figure.
pbc_ggpart <- combine.gg_partial(gg_dta[[1]], gg_dta[[2]],
lbls = c("1 Year", "3 Years"))
summary(pbc_ggpart)
class(pbc_ggpart[["bili"]])
# Plot the highest ranked variable, by name.
#plot(pbc_ggpart[["bili"]])
# Create a temporary holder and remove the stage and edema data
ggpart <- pbc_ggpart
ggpart$edema <- NULL
# Panel plot the remainder.
plot(ggpart, panel = TRUE)
#plot(pbc_ggpart[["edema"]], panel=TRUE) #,
# notch = TRUE, alpha = .3, outlier.shape = NA)
## End(Not run)
```

gg_partial_coplot.rfsrc
Data structures for stratified partial coplots
#### Description 

Data structures for stratified partial coplots
#### Usage 
<pre><code>

## S3 method for class 'rfsrc'
gg_partial_coplot(object, xvar, groups, surv_type = c("mort",
"rel.freq", "surv", "years.lost", "cif", "chf"), time, ...)

</code></pre>
#### Arguments

object rfsrc object
gg_partial_coplot.rfsrc 21
xvar list of partial plot variables
groups vector of stratification variable.
surv_type for survival random forests, c("mort", "rel.freq", "surv", "years.lost", "cif", "chf")
time vector of time points for survival random forests partial plots.
... extra arguments
 passed to plot.variable function
Value
gg_partial_coplot object. An subclass of a gg_partial_list object
#### Examples 
```{r} 

## Not run:
# Load the forest
data(rfsrc_pbc, package="ggRandomForests")
# Create the variable plot.
ggvar <- gg_variable(rfsrc_pbc, time = 1)
# Find intervals with similar number of observations.
copper_cts <-quantile_pts(ggvar$copper, groups = 6, intervals = TRUE)
# Create the conditional groups and add to the gg_variable object
copper_grp <- cut(ggvar$copper, breaks = copper_cts)
## End(Not run)
## Not run:
## We would run this, but it's expensive
partial_coplot_pbc <- gg_partial_coplot(rfsrc_pbc, xvar = "bili",
groups = copper_grp,
surv_type = "surv",
time = 1,
show.plots = FALSE)
## End(Not run)
## Not run:
## so load the cached set
data(partial_coplot_pbc, package="ggRandomForests")
# Partial coplot
plot(partial_coplot_pbc) #, se = FALSE)
## End(Not run)
```

gg_rfsrc.rfsrc Predicted response data object
#### Description 

Extracts the predicted response values from the rfsrc object, and formats data for plotting the
response using plot.gg_rfsrc.
#### Usage 
<pre><code>

## S3 method for class 'rfsrc'
gg_rfsrc(object, oob = TRUE, by, ...)

</code></pre>
#### Arguments

object rfsrc object
oob boolean, should we return the oob prediction , or the full forest prediction.
by stratifying variable in the training dataset, defaults to NULL
... extra arguments

Details
surv_type ("surv", "chf", "mortality", "hazard") for survival forests
oob boolean, should we return the oob prediction , or the full forest prediction.
Value
gg_rfsrc object
See Also
plot.gg_rfsrc rfsrc plot.rfsrc gg_survival
#### Examples 
```{r} 

## ------------------------------------------------------------
## classification example
## ------------------------------------------------------------
## -------- iris data
rfsrc_iris <- rfsrc(Species ~ ., data = iris)
#data(rfsrc_iris, package="ggRandomForests")
gg_dta<- gg_rfsrc(rfsrc_iris)
plot(gg_dta)
## ------------------------------------------------------------
## Regression example
## ------------------------------------------------------------
gg_rfsrc.rfsrc 23
## Not run:
## -------- air quality data
# rfsrc_airq <- rfsrc(Ozone ~ ., data = airquality, na.action = "na.impute")
data(rfsrc_airq, package="ggRandomForests")
gg_dta<- gg_rfsrc(rfsrc_airq)
plot(gg_dta)
## End(Not run)
## Not run:
## -------- Boston data
data(rfsrc_Boston, package="ggRandomForests")
plot(rfsrc_Boston)
## End(Not run)
## Not run:
## -------- mtcars data
data(rfsrc_mtcars, package="ggRandomForests")
gg_dta<- gg_rfsrc(rfsrc_mtcars)
plot(gg_dta)
## End(Not run)
## ------------------------------------------------------------
## Survival example
## ------------------------------------------------------------
## Not run:
## -------- veteran data
## randomized trial of two treatment regimens for lung cancer
# data(veteran, package = "randomForestSRC")
# rfsrc_veteran <- rfsrc(Surv(time, status) ~ ., data = veteran, ntree = 100)
data(rfsrc_veteran, package = "ggRandomForests")
gg_dta <- gg_rfsrc(rfsrc_veteran)
plot(gg_dta)
gg_dta <- gg_rfsrc(rfsrc_veteran, conf.int=.95)
plot(gg_dta)
gg_dta <- gg_rfsrc(rfsrc_veteran, by="trt")
plot(gg_dta)
## End(Not run)
## Not run:
## -------- pbc data
## We don't run this because of bootstrap confidence limits
data(rfsrc_pbc, package = "ggRandomForests")
## End(Not run)
## Not run:
gg_dta <- gg_rfsrc(rfsrc_pbc)
plot(gg_dta)
gg_dta <- gg_rfsrc(rfsrc_pbc, conf.int=.95)
24 gg_roc.rfsrc
plot(gg_dta)
## End(Not run)
## Not run:
gg_dta <- gg_rfsrc(rfsrc_pbc, by="treatment")
plot(gg_dta)
## End(Not run)
```

``gg_roc.rfsrc`` ROC (Receiver operator curve) data from a classification random forest.
#### Description 

The sensitivity and specificity of a randomForests classification object.
#### Usage 
<pre><code>

## S3 method for class 'rfsrc'
gg_roc(object, which.outcome, oob = TRUE, ...)

</code></pre>
#### Arguments

object an rfsrc classification object
which.outcome select the classification outcome of interest.
oob use oob estimates (default TRUE)
... extra arguments
 (not used)

#### Value
gg_roc data.frame for plotting ROC curves.
See Also
plot.gg_roc rfsrc
#### Examples 
```{r} 

## ------------------------------------------------------------
## classification example
## ------------------------------------------------------------
## -------- iris data
rfsrc_iris <- rfsrc(Species ~ ., data = iris)
#data(rfsrc_iris, package="ggRandomForests")
# ROC for setosa
gg_survival 25
gg_dta <- gg_roc(rfsrc_iris, which.outcome=1)
plot(gg_dta)
# ROC for versicolor
gg_dta <- gg_roc(rfsrc_iris, which.outcome=2)
plot(gg_dta)
# ROC for virginica
gg_dta <- gg_roc(rfsrc_iris, which.outcome=3)
plot(gg_dta)
gg_survival Nonparametric survival estimates.
#### Description 

Nonparametric survival estimates.
#### Usage 
<pre><code>

gg_survival(interval = NULL, censor = NULL, by = NULL, data,
type = c("kaplan", "nelson"), ...)

</code></pre>
#### Arguments

interval name of the interval variable in the training dataset.
censor name of the censoring variable in the training dataset.
by stratifying variable in the training dataset, defaults to NULL
data name of the training data.frame
type one of ("kaplan","nelson"), defaults to kaplan-meier
... extra 
</code></pre>
#### Arguments
 passed to kaplan or nelson functions.
Details
gg_survival is a wrapper function for generating nonparametric survival estimates using either
nelson-aalen or kaplan-meier estimates.
Value
A gg_survival object created using the non-parametric kaplan-meier or nelson-aalon estimators.
See Also
kaplan nelson plot.gg_survival

#### Examples 
```{r} 

## Not run:
## -------- pbc data
data(pbc, package="randomForestSRC")
pbc$time <- pbc$days/364.25
# This is the same as kaplan
gg_dta <- gg_survival(interval="time", censor="status",
data=pbc)
plot(gg_dta, error="none")
plot(gg_dta)
# Stratified on treatment variable.
gg_dta <- gg_survival(interval="time", censor="status",
data=pbc, by="treatment")
plot(gg_dta, error="none")
plot(gg_dta)
# ...with smaller confidence limits.
gg_dta <- gg_survival(interval="time", censor="status",
data=pbc, by="treatment", conf.int=.68)
plot(gg_dta, error="lines")
## End(Not run)
```









shift lead function to shift by one (or more).
#### Description 

lead function to shift by one (or more).
#### Usage 
<pre><code>

shift(x, shift_by = 1)

</code></pre>
#### Arguments

x a vector of values
shift_by an integer of length 1, giving the number of positions to lead (positive) or lag
(negative) by
62 surface_matrix
Details
Lead and lag are useful for comparing values offset by a constant (e.g. the previous or next value)
Taken from: http://ctszkin.com/2012/03/11/generating-a-laglead-variables/
This function allows me to remove the dplyr::lead depends. Still suggest for vignettes though.
#### Examples 
```{r} 

d<-data.frame(x=1:15)
#generate lead variable
d$df_lead2<-ggRandomForests:::shift(d$x,2)
#generate lag variable
d$df_lag2<-ggRandomForests:::shift(d$x,-2)
```

surface_matrix Construct a set of (x, y, z) matrices for surface plotting a
gg_partial_coplot object
#### Description 

Construct a set of (x, y, z) matrices for surface plotting a gg_partial_coplot object
#### Usage 
<pre><code>

surface_matrix(dta, xvar)

</code></pre>
#### Arguments

dta a gg_partial_coplot object containing at least 3 numeric columns of data
xvar a vector of 3 column names from the data object, in (x, y, z) order

#### Details
To create a surface plot, the plot3D::surf3D function expects 3 matrices of n.x by n.y. Take the
p+1 by n gg_partial_coplot object, and extract and construct the x, y and z matrices from the
provided xvar column names.
#### Examples 
```{r} 

## Not run:
## From vignette(randomForestRegression, package="ggRandomForests")
##
data(rfsrc_Boston)
rm_pts <- quantile_pts(rfsrc_Boston$xvar$rm, groups=49, intervals=TRUE)
# Load the stored partial coplot data.
data(partial_Boston_surf)
# Instead of groups, we want the raw rm point values,
# To make the dimensions match, we need to repeat the values
# for each of the 50 points in the lstat direction
rm.tmp <- do.call(c,lapply(rm_pts,
function(grp){rep(grp, length(partial_Boston_surf))}))
# Convert the list of plot.variable output to
partial_surf <- do.call(rbind,lapply(partial_Boston_surf, gg_partial))
# attach the data to the gg_partial_coplot
partial_surf$rm <- rm.tmp
# Transform the gg_partial_coplot object into a list of three named matrices
# for surface plotting with plot3D::surf3D
srf <- surface_matrix(partial_surf, c("lstat", "rm", "yhat"))
## End(Not run)
## Not run:
# surf3D is in the plot3D package.
library(plot3D)
# Generate the figure.
surf3D(x=srf$x, y=srf$y, z=srf$z, col=topo.colors(10),
colkey=FALSE, border = "black", bty="b2",
shade = 0.5, expand = 0.5,
lighting = TRUE, lphi = -50,
xlab="Lower Status", ylab="Average Rooms", zlab="Median Value"
)
## End(Not run)
```